---
title: "Relationship between Amount Spent on Wine and Other Aspects - Checkpoint 3"
date: "2021/12/7"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r message=FALSE, warning=FALSE, ,echo=FALSE, include=FALSE, paged.print=FALSE}
wd <- getwd()
setwd(wd) ## set working directory
library(lubridate)
library(tidyverse)
library(caret)
```


**This document is made for displaying the code we used, and the formal final report is the other file.\



```{r echo=FALSE, out.width="50%"}
wine <- read.delim("./marketing_campaign.csv")


qplot(wine$Income * 0.001
      , wine$MntWines * 0.001,
      xlim = c(0,200),
      main = "Income vs Money Spent on Wine in 1000 dollars",
      xlab = "Customer's yearly household income",
      ylab = "Amount spent on wine")



qplot(wine$MntMeatProducts * 0.001
      , wine$MntWines * 0.001,
      main = "Money Spent on Meat Product vs on Wine in 1000 dollars",
      xlab = "Amount spent on meat in last 2 years",
      ylab = "Amount spent on wine")



```

``` {r, out.width="150%"}
newwine <- wine[,c(2,5,9,10,11,12,13,14,15,16)]
cormat <- round(cor(newwine),2)
library(reshape2)
melted_cormat <- melt(cormat)
head(melted_cormat)

library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

```




```{r echo=FALSE}
library(olsrr)
model1 <- lm(MntWines ~ Year_Birth + Education +
               Marital_Status  + Income + Kidhome +
               Teenhome + Recency + MntFruits +
               MntMeatProducts + MntFishProducts + MntSweetProducts +
               MntGoldProds + NumDealsPurchases, data = wine)
ols_step_both_p(model1)


```
\
It seems like "MntSweetProducts" has the smallest risk.\
We apply best subsets regression method, and focus on $Cp$ and $AIC$, and temporarily ignore the other columns in the output , also the off-screen part.\
\

```{r}
library(tidyverse)
library(mgcv)
library(randomForest)
library(testthat)
ntrees <- 200
rf <- randomForest(MntWines ~.,
                   data = newwine,
                   ntree = ntrees,
                   na.action = na.omit,
                   type = classification)
print(rf)
varImpPlot(rf, main = "Variable Importance plot")

```


```{r}
model2 <- lm(MntWines ~ Income + MntMeatProducts + Kidhome +
               Education + MntGoldProds + NumDealsPurchases + MntSweetProducts, data = wine)
k <- ols_step_best_subset(model2)
k
```


\
Next, we plot risk against different possible models (in the table above) as follows:\
\

```{r fig.align="center"}

plot(k)

```
\
We conclude that a combination of "Income", "MntMeatProducts", "Kidhome", "Education", "MntGoldProds", "NumDealsPurchases", and "MntSweetProducts", is the best choice due to its lowest $Cp$ and $AIC$.\
\
Below, we use the selected variables above to fit a ordinary linear model, and analyze it by shrinkage methods Ridge and Lasso.
\

```{r}
library(glmnet)
ols <- lm(MntWines ~ Income + MntMeatProducts + Kidhome + Education + 
             MntGoldProds + NumDealsPurchases + MntSweetProducts,
          data = wine)
x <- model.matrix(ols) 
y <- wine$MntWines[-ols$na.action] # remove those observations with missing values. glmnet() hates those. They are already dropped in x.
ridge <- cv.glmnet(x, y, alpha = 0)
lasso <- cv.glmnet(x, y)
plot(lasso, main = "CV score for Lasso")
```
